# Results

## Existing scenario evaluation
UTA, in partnership with VIA, ran a pilot program of microtransit service in south Salt Lake County from December 2019--November 2020. We also created a scenario in BEAM to model this pilot program. In order to assess the performance of our BEAM simulations when compared with real-world observed data, we compared the results of the two on several metrics (Table \@ref(tab:existing-comparison)).

```{r existing-comparison}
tar_load(existing_comparison)

existing_comparison %>%
  kbl(booktabs = TRUE, digits = c(0,0,2,1),
      caption = "Comparison of Observed Data with 'Existing' BEAM Scenario") %>%
  kable_styling()
```

At first glance, these results seem to be quite good, as the simulated scenario reports nearly identical metrics to the real-world data. However, it is important to consider that our model scenario uses a 20% population sample, and the observed data reflects the entire population.


## Candidate scenario comparison
We then ran each of our scenarios as described in section \@ref(scenario-configuration), and compared several metrics. These metrics include total ridership, utilization, and wait time, as in the previous comparison, but also includes <><Other metrics><>. These comparisons are given in Tables \@ref(tab:ridership-compare)--\@ref(tab:wait-time-compare).

```{r ridership-compare}
tar_read(ridership_comparison) %>% 
  kbl(booktabs = TRUE, digits = 0,
      caption = "Comparison of Weekday Ridership Across Scenarios") %>% 
  kable_styling()
```

```{r util-compare}
tar_read(utilization_comparison) %>% 
  kbl(booktabs = TRUE, digits = 2,
      caption = "Comparison of Utilization Across Scenarios") %>% 
  kable_styling()
```

```{r wait-time-compare}
tar_read(wait_time_comparison) %>% 
  kbl(booktabs = TRUE, digits = 2,
      caption = "Comparison of Wait Times Across Scenarios") %>% 
  kable_styling()
```


It is clear that in the scenarios with more microtransit vehicles available, ridership greatly increases. Interestingly, utilization does not vary much at all, which implies that at least in these specific scenarios there is a roughly linear relationship between number of vehicles and number of riders. Wait times also hardly are affected in the various scenarios.

## Summary

More Text
